SCP Briefing Plots - Combined Intervention

### 2024-08-05 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Minor path changes to vis script for relative and absolute together intervention

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { 
    tit <- 'Whole Population'
    plot_colour <- 'black'
    }
  if (summary_group == 'families') { 
    tit <- 'Families'
    plot_colour <- '#56B4E9'
    }
  if (summary_group == 'treated_relative') { 
    tit <- 'Treated' }
  if (summary_group == 'treated_absolute') { 
    tit <- 'Treated' }
  if (summary_group == 'priority_any') { 
    tit <- 'Any Priority Subgroup' 
    plot_colour <- 'black' }

@@

```{r}
SF12_change_income_quint(summary_group = 'whole_pop',
                                    scen.list = scen.list)
# SF12_change_income_quint2(summary_group = 'whole_pop',
#                                     scen = scen)
```

@@

```{r}
# SF12_change_income_quint(summary_group = 'families',
#                                     scen.list = scen.list.rel)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = scen)
```

@@

```{r}
# SF12_change_simple(summary_group = 'treated_relative',
#                    scen.list = scen.list.rel)

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_27_scot_XGB_scaled/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_28_scot_scaled_GOOD/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old_29_scot_scaled_skew_GOOD/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { 
    tit <- 'Whole Population'
    plot_colour <- 'black'
    }
  if (summary_group == 'families') { 
    tit <- 'Families'
    plot_colour <- '#56B4E9'
    }
  if (summary_group == 'treated_relative') { 
    tit <- 'Treated'
    plot_colour <- 'black'}
  if (summary_group == 'treated_absolute') { 
    tit <- 'Treated'
    plot_colour <- 'black'}
  if (summary_group == 'priority_any') { 
    tit <- 'Any Priority Subgroup' 
    plot_colour <- 'black' }

@@

```{r}
SF12_change_income_quint(summary_group = 'whole_pop',
                                    scen.list = scen.list)
SF12_change_income_quint2(summary_group = 'whole_pop',
                                    scen = scen)
```

@@

```{r}
SF12_change_income_quint(summary_group = 'families',
                                    scen.list = scen.list)
SF12_change_income_quint2(summary_group = 'families',
                                    scen = scen)
```

@@

```{r}
SF12_change_simple(summary_group = 'treated_relative',
                   scen.list = scen.list)

SF12_change_simple(summary_group = 'treated_absolute',
                   scen.list = scen.list)
